fromFobLisa, Version 2

### 2018-03-03 CreData/fromFobLisa.Rmd
continuing

---
title: "fromFobLisa, Version 2"
author: "Göran Broström"
date: "March 1, 2018"
output: pdf_document
fontsize: 11pt
---

@@

```{r days}
ar <- seq(1960, 1990, by = 5)
days <- as.numeric(skum::tillTid(paste(ar, "1101", sep = "")))
days
```

@@

Note that this is per year.

## FoB 1960

Persons in the fob and in our KOMMUNer.

```{r fob60}
load("../../Data/fob.rda")
fob60 <- fob[fob$AR == 1960 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

They need to be of the right age (born on November 1, 1940 or earlier). We
get the birthdates from *inddata*.

```{r mat60}
library(eha)
indx <- match(fob60$LINNEID, per$LINNEID)
fob60$birthdate <- per$birthdate[indx]
fob60$fobdate <- as.numeric(toTime("1960-11-01"))
##lim <- as.numeric(toTime("1940-11-01"))
##fob60 <- fob60[fob60$birthdate < lim, ]
indx <- match(fob60$LINNEID, per$LINNEID) # NOTE: Necessary!
fob60$enter <- fob60$fobdate - fob60$birthdate
dd <- per$deathdate[indx]
##fob60$event <- !(is.na(dd)) & (dd <= lim + 25) # NOTE: 40 --> 25!
fob60$event <- !(is.na(dd)) & (dd <= fob60$fobdate +5)
fob60$exit <- fob60$enter + 5
fob60$exit[fob60$event] <- dd[fob60$event] - fob60$birthdate[fob60$event]
head(fob60)
```

## FoB 1965

Persons in the fob and in our KOMMUNer.

```{r fob65}
fob65 <- fob[fob$AR == 1965 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

They need to be of the right age (born on November 1, 1930 or earlier). We
get the birthdates from *inddata*.

```{r mat65}
library(eha)
indx <- match(fob65$LINNEID, per$LINNEID)
fob65$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1945-11-01"))
fob65 <- fob65[fob65$birthdate < lim, ]
indx <- match(fob65$LINNEID, per$LINNEID) # NOTE: Necessary!
fob65$enter <- lim + 20 - fob65$birthdate
dd <- per$deathdate[indx]
fob65$event <- !(is.na(dd)) & (dd <= lim + 25) ## NOTE: 40 --> 25!
fob65$exit <- fob65$enter + 5
fob65$exit[fob65$event] <- dd[fob65$event] - fob65$birthdate[fob65$event]
fob65 <- fob65[fob65$exit > fob65$enter, ] # Shouldn't be necessary!
head(fob65)
```

It should be noted that three persons present in the 1965 FoB actually died 1964 or earlier.

## FoB 1970

Persons in the fob and in our KOMMUNer.

```{r fob70}
fob70 <- fob[fob$AR == 1970 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

They need to be of the right age (born on November 1, 1935 or earlier). We
get the birthdates from *inddata*.

```{r mat70}
library(eha)
indx <- match(fob70$LINNEID, per$LINNEID)
fob70$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1950-11-01"))
fob70 <- fob70[fob70$birthdate <= lim, ]
indx <- match(fob70$LINNEID, per$LINNEID) # NOTE: Necessary!
fob70$enter <- lim + 20 - fob70$birthdate
dd <- per$deathdate[indx]
fob70$event <- !(is.na(dd)) & (dd <= lim + 25)
fob70$exit <- fob70$enter + 5
fob70$exit[fob70$event] <- dd[fob70$event] - fob70$birthdate[fob70$event]
fob70 <- fob70[fob70$exit > fob70$enter, ] # Shouldn't be necessary!
head(fob70)
cat("lim = ", lim, "\n")
```

It should be noted that one person present in the 1970 FoB actually died 1964.

## FoB 1975

Persons in the fob and in our KOMMUNer.

```{r fob75}
fob75 <- fob[fob$AR == 1975 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

They need to be of the right age (born on November 1, 1940 or earlier). We
get the birthdates from *inddata*.

```{r mat75}
library(eha)
indx <- match(fob75$LINNEID, per$LINNEID)
fob75$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1955-11-01"))
fob75 <- fob75[fob75$birthdate < lim, ]
indx <- match(fob75$LINNEID, per$LINNEID) # NOTE: Necessary!
fob75$enter <- lim + 20 - fob75$birthdate
dd <- per$deathdate[indx]
fob75$event <- !(is.na(dd)) & (dd <= lim + 25)
fob75$exit <- fob75$enter + 5
fob75$exit[fob75$event] <- dd[fob75$event] - fob75$birthdate[fob75$event]
fob75 <- fob75[fob75$exit > fob75$enter, ] # Shouldn't be necessary!
head(fob75)
##cat("lim = ", lim, "\n")
```

It should be noted that one person present in the 1975 FoB actually died 1964 (same person as earlier).

## FoB 1980

Persons in the fob and in our KOMMUNer.

```{r fob80}
fob80 <- fob[fob$AR == 1980 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

They need to be of the right age (born on November 1, 1945 or earlier). We
get the birthdates from *inddata*.

```{r mat80}
library(eha)
indx <- match(fob80$LINNEID, per$LINNEID)
fob80$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1960-11-01"))
fob80 <- fob80[fob80$birthdate < lim, ]
indx <- match(fob80$LINNEID, per$LINNEID) # NOTE: Necessary!
fob80$enter <- lim + 20 - fob80$birthdate
dd <- per$deathdate[indx]
fob80$event <- !(is.na(dd)) & (dd <= lim + 25)
fob80$exit <- fob80$enter + 5
fob80$exit[fob80$event] <- dd[fob80$event] - fob80$birthdate[fob80$event]
fob80 <- fob80[fob80$exit > fob80$enter, ] # Shouldn't be necessary!
head(fob80)
##cat("lim = ", lim, "\n")
```

It should be noted that one person present in the 1980 FoB actually died 1964 (same person as earlier).

## FoB 1985

This is no longer the last FoB we are using: The follow-up time this time
*is* five years (as before), but five years, from November 1, 1985 to October 31, 1990, when the *lisa* data fills in.

Persons in the fob and in our KOMMUNer.

```{r fob85}
fob85 <- fob[fob$AR == 1985 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

They need to be of the right age (born on November 1, 1950 or earlier). We
get the birthdates from *inddata*.

```{r mat85}
library(eha)
indx <- match(fob85$LINNEID, per$LINNEID)
fob85$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1965-11-01"))
fob85 <- fob85[fob85$birthdate < lim, ]
indx <- match(fob85$LINNEID, per$LINNEID) # NOTE: Necessary!
fob85$enter <- lim + 20 - fob85$birthdate
##fob85$enter <- as.numeric(toTime("1985-11-01")) - fob85$birthdate
dd <- per$deathdate[indx]
fob85$event <- !(is.na(dd)) & (dd <= lim + 25)
##fob85$event <- !(is.na(dd)) & (dd < 1987) 
fob85$exit <- fob85$enter + 5  ## Not any longer: 1 year and 2 months.
fob85$exit[fob85$event] <- dd[fob85$event] - fob85$birthdate[fob85$event]
fob85 <- fob85[fob85$exit > fob85$enter, ] # Shouldn't be necessary!
head(fob85)
##cat("lim = ", lim, "\n")
```

It should be noted that one person present in the 1985 FoB actually died 1964 (same person as earlier).

## FoB 1990

This is no longer the last FoB we are using: The follow-up time this time
*is* ten years (as before), from November 1, 1990 to October 31, 2000, when
the *lisa* data has been filling in for a long time.

Persons in the fob and in our KOMMUNer.

```{r fob90}
fob90 <- fob[fob$AR == 1990 & 
                 fob$KOMMUN %in% ourkom &
                 fob$LINNEID %in% per$LINNEID, ]
```

They need to be of the right age (born on November 1, 1960 or earlier). We
get the birthdates from *inddata*.

```{r mat90}
library(eha)
indx <- match(fob90$LINNEID, per$LINNEID)
fob90$birthdate <- per$birthdate[indx]
lim <- as.numeric(toTime("1960-11-01"))
fob90 <- fob90[fob90$birthdate < lim, ]
indx <- match(fob90$LINNEID, per$LINNEID) # NOTE: Necessary!
fob90$enter <- lim + 20 - fob90$birthdate
##fob90$enter <- as.numeric(toTime("1985-11-01")) - fob85$birthdate
dd <- per$deathdate[indx]
fob90$event <- !(is.na(dd)) & (dd <= lim + 20)
##fob90$event <- !(is.na(dd)) & (dd < 1987) 
fob90$exit <- fob90$enter + 10  ## Not any longer: 1 year and 2 months.
fob90$exit[fob90$event] <- dd[fob90$event] - fob90$birthdate[fob90$event]
fob90 <- fob90[fob90$exit > fob90$enter, ] # Shouldn't be necessary!
head(fob90)
##cat("lim = ", lim, "\n")
```

It should be noted that one person present in the 1985 FoB actually died 1964 (same person as earlier).

This ends the data collection from the FoBs. Remains to put all together.

## Putting the data from all FoBs in one data frame

We put the event histories described by the FoBs (with FoB90!) into one data frame.

```{r fobgrab}
fobdata <- rbind(fob60, fob65, fob70, fob75, fob80, fob85, fob90)
fobdata <- fobdata[order(fobdata$LINNEID, fobdata$enter), ]
##fobdata <- age.window(fobdata, c(40, 110))
rownames(fobdata) <- 1:NROW(fobdata)
save(fobdata, file = "fobdata.rda")
```

>>>>

---
title: "fromFobLisa, Version 2"
author: "Göran Broström"
date: "March 1, 2018"
output:
  html_document:
    df_print: paged
fontsize: 11pt
---

@@

```{r days}
load("../../Data/fob.rda")
ar <- seq(1960, 1990, by = 5)
days <- as.numeric(skum::tillTid(paste(ar, "1101", sep = "")))
days
```

@@

Get `birthdate` from `per`.

```{r getbirthdateanddathdate}
indx <- match(fob$LINNEID, per$LINNEID)
fob$birthdate <- per$birthdate[indx]
fob$deathdate <- per$deathdate[indx]
```

Create individual Fobs (1960, 1965, etc):

```{r rawfob}
source("R/extractFob.R")
n <- length(ar)
fobbar <- vector(mode = "list", length = n)
names(fobbar) <- paste("fob", (ar %% 100), sep = "")
for (i in 1:(n-1)){
    fobbar[[i]] <- extractFob(ar[i], followUp = 5, data = fob)
}
fobbar[[n]] <- extractFob(ar[n], followUp = 11 + 61 / 365, data = fob)
fobdata <- do.call(rbind, fobbar)
fobdata <- fobdata[order(fobdata$LINNEID, fobdata$enter), ]
##fobdata <- age.window(fobdata, c(40, 110))
rownames(fobdata) <- 1:NROW(fobdata)
save(fobdata, file = "fobdata2.rda")
```
